upwell_IDX

### 2019-08-20 upwell_IDX.Rmd
fixed

>>>>

# Wind speed intensifed ovwer the years
Take first third (33percentile) of the data and the last third (66th percentile) of the data for every season and then do a t-test

```{r}
load("Data/wind_daily.RData")

wind_daily <- wind_daily %>% 
  dplyr::rename(t = date)

# wind_daily_season <- season_func(df = wind_daily)

#save(wind_daily_season, file = "Data/wind_daily_season.RData")

load("Data/wind_daily_season.RData")

wind_daily_season_test <- wind_daily_season %>% 
  group_by(season, temp_sites) %>% 
  arrange(mean_speed) %>% 
  summarize(msp_1st = quantile(mean_speed, probs=0.33, na.rm=TRUE),
            mspeed_2nd = quantile(mean_speed, probs=0.66, na.rm=TRUE))

# T-test

# T- test between seasons for all sites

```
